The hedging hyperprior for the normal distribution: known mean, unknown precision

### 2023-03-16 text/23/normal-hedging-hyperprior-part-2.Rmd
Added gamma distribution to normal-heding-prior-part-2

---
title: "The hedging hyperprior for the normal distribution: known mean, unknown precision"
source: "New"
date: "2023-02-28"
categories:
- Blog post
tags:
- Bayesian statistics
output: html_document
---

@@

@@

$f(X; \mu, \tau) = \sqrt{\frac{\tau}{2 \pi}}e^{-(X-\mu)^2 / 2\sigma^2}$

@@

Assume that $\tau$ is known and equal to $\tau_F$. A more general case, with $\tau$ unknown is described on a separate web page. For simplicity, we will drop any multiplicative constants not involving X or $\mu$

$f(X; \mu) \propto e^{-\frac{1}{2}\tau_F(X-\mu)^2}$

The conjugate prior for a normal distribution is also a normal distribution.

$g(\mu; \mu_0, \tau_0) \propto e^{- \frac{1}{2}\tau_0(\mu-\mu_0)^2}$

where the prior mean is $\mu_0$ and the prior precision is $\tau_0$.

For an informative prior distribution, $\tau_0$ is usually much smaller than $\tau_F$. The ratio $n_0=\tau_F/\tau_0$ is the effective prior sample size and is equivalent to adding $n_0$ pseudo data values of $\mu_0$ to the observed data.

>>>>

---
title: "The hedging hyperprior for the normal distribution: known mean, unknown precision"
source: "New"
date: "2023-03-14"
categories:
- Blog post
tags:
- Bayesian statistics
output: html_document
---

@@

$f(X; \mu, \sigma) = \frac{\tau}{\sigma sqrt{2 \pi}}e^{-(X-\mu)^2 / 2\sigma^2}$

@@

$f(X; \mu, \tau) = \sqrt{\frac{\tau}{2 \pi}}e^{-\frac{1}{2}\tau (X-\mu)^2}$

@@

Assume that $\mu$ is known and equal to $\mu_F$. An earlier case with $\tau$ known and $\mu$ unknown appears on a different web page. A more general case, with both $\mu$ and $\tau$ unknown is also described on a separate web page. For simplicity, we will drop any multiplicative constants not involving X or $\tau$

$f(X; \tau) \propto \sqrt{\tau}e^{-\frac{1}{2}\tau(X-\mu_F)^2}$

The conjugate prior for a normal distribution is a gamma distribution.

$g(\tau; \alpha_0, \beta_0) \propto \frac{\beta_0^\alpha_0}{\Gamma(\alpha)} \tau^{\alpha-1} e^{-\beta \tau}$

$\beta_0 = 1 / \tau_0$

For an informative prior distribution, $\alpha$ is large. This prior is is equivalent to adding $n_0$ pseudo data values of $\tau_0$ to the observed data.
